worldmap

### 2024-11-18 analysis/figures/visualization.Rmd
Don't need this any more

```
Plots of significant contrasts
```{r}
contrast_data <- model_output %>%
  filter(metric %in% c("Jaccard_base", "CWM_diet_vfish", "CWM_diet_vunk"), 
         model_id != "base", 
         effect %in% c("fixed", "contrast", "group_slope")) %>%
  select(effect, term, estimate, p.adjust, metric, model_id)

# test to plot taxa models
test_plot_data <- contrast_data %>%
  filter(model_id == "taxa", metric == "Jaccard_base")

bird_params <- list(slope = test_plot_data %>% filter(term == "Birds") %>% pull(estimate),
                    intercept = test_plot_data %>% filter(term == "(Intercept)") %>% pull(estimate),
                    sig = test_plot_data %>% filter(term == "Birds") %>% pull(p.adjust) < 0.05)
mammal_params <- list(slope = test_plot_data %>% filter(term == "Mammals") %>% pull(estimate),
                      intercept = (test_plot_data %>% filter(term == "taxaMammals") %>% pull(estimate) + 
                                     bird_params$intercept))
ggplot() + theme_minimal() +
  xlim(0, 1) +
  ylim(0, 3) +
  geom_abline(slope = bird_params$slope, intercept = bird_params$intercept, color = "red") +
  geom_abline(slope = mammal_params$slope, intercept = mammal_params$intercept,)

model_data %>%
  filter(taxa != "Amphibians", metric == "Jaccard_base") %>%
  ggplot(aes(x = year_scaled, y = value, color = taxa)) +
  geom_point() +
  geom_abline(slope = -0.033233485, intercept = 0.42832, color = "red") +
  geom_abline(slope = -0.026364796, intercept = 0.42832 + 0.095965269)
```
Let's try dot plots of each categorical slope
```{r}
library(patchwork)

>>>>

```

Let's try dot plots of each categorical slope
```{r}
library(patchwork)
